\chapter{Summary}
In this final chapter, I conclude by describing the progress made towards researching the field of programing by using natural language in terms of the prototype development, the experiments that we carried out, the concepts that have been developed, and additional products that were developed during the research. I also suggest some future research directions that could provide the next steps along the path to a practical and widely applicable programming systems.

We have explored the domain of software development tools and programming environments. We have developed a concept enabling the programmer to use mobile devices as programming environments in addition to PCs and laptops. We encountered a number of questions that we had to answer before starting to develop a concept and a prototype for such an idea. What language are we going to use? How will the code be represented on small screens?  How will the programmer interact with the mobile device?

After finding solutions to all those questions we decided that we need to do a set of experiments to understand how a programmer interacts with a programming environment when she needs to use her voice. Following the experiments we extracted the most significant information in order to understand how programmers tend to describe the code that they want to write. The information that we extracted is essential for this study because it allowed us to determine the best direction concerning how to proceed with the study.

After we have completed the experiments, we decided that we need to explore the existing programming environments and features in different programming languages, especially Java. We collected a huge set of programming features, which we will need in future work in order to expand the usability of the application that will be built.

Based on the features that we have collected, we have developed a series of concepts of how code may be represented on a small screen (mobile phones and tablets). Those concepts may be used in future work to complete the prototype and to prove that development on mobile devices using voice and touch is feasible.
We had the idea of allowing every programmer to configure the representation of the code that makes the most sense to him or her. Meaning, a programmer would be able to configure the representation of the code that would be easier for his or her understanding. This is a very advanced idea and not easy for implementation, but we managed to develop a fundamental concept of how it may work.

As mentioned, we found that in order to allow the programmer to code on mobile devices we have to develop programming by voice. Therefore, we researched related works, available systems and tools, and developed two modules: a speech to text engine, based on Google Speech Server, and a context free grammar parser and lexer --- we used Antlr4 for this. Those two modules will be used in future work.

For future work we plan to use the modules that already have been developed and to develop an IDE for devices. In particular, we need to develop an interface for PCs and laptops and afterwards on mobile devices. This interface needs to be integrated with the \textit{Dictation Parser} and the \textit{Speech to Text}. In addition, the Parser and Lexer are designed and written in such a way so it will be very easy to expand their usability. Regarding the \textit{Speech to Text}, its performance depends on Google's server performance which is not always has a fast responses and limited to 50 requests per day, meaning we may exchange it with other speech to text module. The one that we are aiming for now is IBM Watson (\href{https://www.ibm.com/smarterplanet/us/en/ibmwatson/developercloud/}{link}). Additional future work is to make this system works for other languages e.g., C++.

We published and presented a paper in the MobileSoft Conference which is part of the ICSE conference took place in Florence in May 2015.

All projects are committed to GitHub (\href{https://github.com/shaolinrabbi/DeveryWhere.git}{link to the repository on GitHub}) and they are public, which means every programmer is able to connect to that repository and contribute as he or she wishes.